\documentclass[../main.tex]{subfiles}

\begin{document}

\section{Problem 4.2}

Use separation of variable in \textit{cartesian} coordinates to solve the infinite \textit{cubical} well (or particle in a box):
\begin{gather*}
    V(x,y,z) = 
    \left\{
        \begin{array}{cc}
            0, & \forall x,y,z \in \qty[0,a] \\
            \infty, & \forall x,y,z \notin \qty[0,a] 
        \end{array}
    \right.
\end{gather*}

\begin{enumerate}
    \item Find the stationary states, and the corresponding energies.
    \item Call the distinct energies $E_1,E_2,\dots$ in order of increasing energy.
        Find $E_1,E_2,E_3,E_4,E_5$ and $E_6$.
        Determine their degeneracies (that is, the number of different states that share the same energy).
    \item What is the degeneracy of $E_{14}$, and why is this case interesting?
\end{enumerate}

\begin{sol}{Stationary states}{label-1}
    To find the stationary states of the infinite cubical well, we are going to solve the time independent Schrödinger equation,
    \begin{gather*}
        -\frac{\hbar^2}{2m}\nabla\psi=E\psi,~\forall x,y,z \in \qty[0,a],
    \end{gather*}
    with the following boundary conditions $\psi(0,0,0)=\psi(a,a,a)=0$.
    To solve the equation we are going to use the method of separation of variables, that is, that we assume that the solution of the differential equation has the following form $\psi(x,y,z)=X(x)Y(y)Z(z)$.
    Substituting this solution to the differential equation, we can perfom some algebraic manipulation,
    \begin{gather*}
        -\frac{\hbar^2}{2m}\nabla\psi =E\psi \\
        \qty(\pdv[2]{x}+\pdv[2]{y}+\pdv[2]{z})X(x)Y(y)Z(z) = -\frac{2m}{\hbar^2}EX(x)Y(y)Z(z) \\
        Y(y)Z(z)\pdv[2]{x}X(x)+X(x)Z(z)\pdv[2]{y}Y(y)+X(x)Y(y)\pdv[2]{z}Z(z) = -\frac{2m}{\hbar^2}EX(x)Y(y)Z(z) \\
        \frac{1}{X(x)}\pdv[2]{x}X(x)+\frac{1}{Y(y)}\pdv[2]{y}Y(y)+\frac{1}{Z(z)}\pdv[2]{z}Z(z)= -\frac{2m}{\hbar^2}E.
    \end{gather*}
    Now we can re-write this partial differential equation into three diferential equations assumming that $E=\frac{\hbar^2}{2m}\qty(k_x^2+k_y^2+k_z^2)$,
    \begin{align*}
        \dv[2]{X(x)}{x} = -k_x^2X(x) &\rightarrow X(x)=A_x\sin\qty[k_x x]+B_x\cos\qty[k_x x],\\
        \dv[2]{Y(y)}{y} = -k_y^2Y(y) &\rightarrow Y(y)=A_y\sin\qty[k_y y]+B_y\cos\qty[k_y y],\\
        \dv[2]{Z(z)}{z} = -k_z^2Z(z) &\rightarrow Z(z)=A_z\sin\qty[k_z z]+B_z\cos\qty[k_z z].
    \end{align*}
    In order to find the expression for the coefficients $A_n,~B_n$ and $k_n$, we start by applying the boundary conditions.
    Since $\sin$ and $\cos$ are periodic functions, they satisfy $f(0)=f(a)$, however only the $\sin$ function satisfy the condition $f(0)=f(a)=0$, hence, we set $B_x=B_y=B_z=0$ leading to,
     \begin{gather*}
        X(x)=A_x\sin\qty[k_x x],\quad Y(y)=A_y\sin\qty[k_y y],\quad Z(z)=A_z\sin\qty[k_z z].
    \end{gather*}
    Now we recall the fact that $x,y$ and $z$ have units of distance and that the argument of the $\sin$ function must be dimensonless, combining this restriction with the property of periodicity we can define the constants $k_n$ as, $k_x=n_x\pi/a,~k_y=n_y\pi/a,~k_z=n_z\pi/a$, where $\qty(n_x,n_y,n_z)\in\mathbb{Z}^+$.
    With this information we can re-write the solution as,
    \begin{gather*}
        \psi\qty(x,y,z)=A_x A_y A_z\sin\qty[\frac{n_x\pi}{a} x]\sin\qty[\frac{n_y\pi}{a} y]\sin\qty[\frac{n_z\pi}{a} z],
    \end{gather*} 
    with
    \begin{gather*}
        E=\frac{\pi^2\hbar^2}{2ma^2}\qty(n_x^2+n_y^2+n_z^2), \quad \qty(n_x,n_y,n_z)\in\mathbb{Z}^+.
    \end{gather*}
    Finally, in order to get the expression for $A_x,A_y$ and $A_z$ we apply the normalization restiction to each spatial dimension,
    \begin{align*}
        \int_0^a A_l^2\sin^2\qty[\frac{n_l\pi}{a} s] ds &= A^2_l\frac{a}{4}\qty(2-\frac{1}{\pi n}\sin\qty[2\pi n]) = 1,
    \end{align*}
    since $n\in\mathbb{Z}^+$ we get that $A_l=\sqrt{2/a}$, therefore,
    \begin{empheq}[box=\shadowbox]{equation*}
        \psi\qty(x,y,z)=\sqrt{\frac{8}{a^3}}\sin\qty[\frac{n_x\pi}{a} x]\sin\qty[\frac{n_y\pi}{a} y]\sin\qty[\frac{n_z\pi}{a} z], \quad \qty(n_x,n_y,n_z)\in\mathbb{Z}^+
    \end{empheq}
\end{sol}


\begin{sol}{Energy analysis}{label-2}

\end{sol}


\section{Problem 4.3}

Use 
\begin{align*}
    P^m_l(x)&\equiv\qty(1-x^2)^{\abs{m}/2}\qty(\dv{x})^{\abs{m}}P_l(x) \\
    P_l\qty(x) &\equiv\frac{1}{2 l!}\qty(\dv{x})^l\qty(x^2-1)^l \\
    Y^m_l\qty(\theta,\phi) &=\epsilon\sqrt{\frac{\qty(2l+1)}{4\pi}\frac{\qty(l-\abs{m})!}{\qty(l+\abs{m})!}}e^{im\phi}P^m_l\qty(\cos\qty[\theta]) 
\end{align*}
to construct $Y^0_0$ and $Y^l_2$.
Check that they are normalized and orthogonal.

\section{Problem 4.13}

\begin{itemize}
    \item Find $\expval{r}$ and $\expval{r^2}$ for an electron in the ground state of hydrogen.
        Express your answers in terms of the Bohr radius.
    \item Find $\expval{x}$ and $\expval{x^2}$ for an electron in the ground stat of hydrogen.
        \textit{Hint:} this requires no noew integration-note that $r^2=x^2+y^2+z^2$, and explot the symmetry of the ground state.
    \item Find $\expval{x^2}$ in the state $n=2,l=1,m=1$. \textit{Warning:} This state is not symmetrical in $x,y,z$.
        Use $x=r\sin\theta\cos\phi$.
\end{itemize}

\section{Problem 4.14}

What is the \textit{most probable} value of $r$, in the ground state of hydrogen?
(The answer is not zero!)
\textit{Hint:} First ypu must figure out the probability that the electron would be found between $r$ and $r+dr$.

\section{Problem 4.23}

In problem 4.3 you showed that 
\begin{gather*}
    Y^l_2\qty(\theta,\phi) = -\sqrt{\frac{15}{8\pi}}\sin\theta\cos\theta e^{i\phi}.
\end{gather*}
Apply the raising operator to find $Y^2_2\qty(\theta,\phi)$.
Use equation $ A^m_l =\hbar\sqrt{l\qty(l+1)-m\qty(m\pm1)}=\hbar\sqrt{\qty(l\mp m)\qty(l\pm m+1)} $ to get the normalization.

\end{document}
