\documentclass[../main.tex]{subfiles}

\begin{document}


\subsection{Rules of interaction}

The simulation methodology is based on the work presented in\citep{gnanSilicoSynthesisMicrogel2017} and\citep{sorichettiStructureElasticityModel2023}, with the objective of create a representative polymer structure of a hydro-gel and characterize the mechanical response under shear deformation.
This methodology creates the structure by using a mixture of two types of patchy particles.
One type represent a \textit{Crosslinker} and is define with 1 central particle and 4 patches placed at the vertices of a circumscribed tetrahedron. %in the center particle.
The other one represent a \textit{Monomer} define by 1 central particle and 2 patches placed at the poles.
Prior to describe the methodology, it is important to mention that to from now on I will refer to the center particle of the Crosslinker patchy particle as ``CL'' and the patches as ``PA'', naturally, the center particle of the Monomer patchy particle as ``MO'' and the patches as ``PB''.

The interaction between the particles are quite simple, the CL$\longleftrightarrow$MO interaction is repulsive modeled by 
\begin{gather}
    U_{WCA}(r) = 4\epsilon\left[\qty(\frac{\sigma}{r})^{12}-\qty(\frac{\sigma}{r})^6\right]+\epsilon,\quad r\in[0,2^{1/6}\sigma],\label{eqn:CL-MO_interaction}
\end{gather}
and the PA$\longleftrightarrow$PB, PB$\longleftrightarrow$PB interactions are attractive modeled by
\begin{gather}
    U_{\mathrm{patchy}}\qty(r_{\mu\upsilon}) = 2\epsilon_{\mu\upsilon}\left(\frac{\sigma_p^4}{2 r_{\mu\upsilon}^4}-1\right)\exp\left[\frac{\sigma_p}{\qty(r_{\mu\upsilon}-r_{c})}+2\right],\quad r_{\mu\upsilon}\in\qty[0,r_c]. \label{eqn:patch-patch_interaction}
\end{gather}
Interactions between particles not metioned before are nonexistent.
Finally, there is an extra 3-particle interaction that aid to assembly the patchy particle structure according to~\citep{sciortinoThreebodyPotentialSimulating2017} and~\citep{sorichettiStructureElasticityModel2023} defined in terms of~\eqref{eqn:patch-patch_interaction},
\begin{gather}
	U_{\mathrm{swap}}(r) = w\sum_{\lambda,\mu,\upsilon}\epsilon_{\mu\upsilon}U_3\qty(r_{\lambda,\mu})U_3\qty(r_{\lambda,\upsilon}),\quad r_{\mu\upsilon}\in\qty[0,r_c],\label{eqn:swap_interaction}
\end{gather}
where
\begin{gather}
    U_{3} = -U_{\mathrm{patchy}}\qty(r)/\epsilon_{\mu\upsilon},\quad r_{\mu\upsilon}\in\qty[0,r_c].\label{eqn:swapmod_interaction}
\end{gather}

Once we defined the interactions between the particles in the system, we define a simulation protocol divided in the following processes, assembly and shear.
Which are going to be described in the following sections.
After the assembly process, the structure is analyse to see if the structure percolate or not and verify if there are only binary patch-interactions, otherwise we checked the implementation of the potentials or the parameters.
Once the hydro-gel structure meet the requirements we start with the shear process and monitored the temperature and energy to see if the simulaiton was converging.
Once those tests done, the mechanical response was analyze thru the components of the stress tensor and structure characterization.

In the following sections the 

\subsection{Assembly of the network}\label{sec:descriptionSimulation}

It it importante to said that the main difference between the articles cited and the implementation are the absence of FENE bonds and the swelling potential.

because part of the exploration is to analyze what happen in the deformation if the interactions between crosslinker and monomer can swap.

\subsection{Tables}

%To use those potentials in LAMMPS we need to declare the force at a given distance.
%Hence, the gradient in polar coordinates is computed, $\nabla = \partial_{r}\hat{r} + 1/r\partial_\theta$, $\vec{F}=-\nabla U$.


\begin{gather}
\vec{F}_{\mathrm{WCA}}(r) = -\frac{\epsilon}{r}\left[24\qty(\frac{\sigma}{r})^6-48\qty(\frac{\sigma}{r})^{12}\right],\quad r\in\qty[0,2^{1/6}\sigma] 
\end{gather}

%The second term is added, due to the diplacemnt in the WCA potential.

\begin{gather}
    \vec{F}_{\mathrm{patchy}}(r) =-\left\{ -\frac{\epsilon\sigma_p}{r^5\qty(r-r_c)^2} \left[ 4r_c^2\sigma^3_p + \sigma^3_p\qty(\sigma_p-8r_c) r -2r^5 + 4r^2 \sigma^3_p \right] \exp\left[\frac{\sigma_p}{r-r_c}+2\right]\right\},\quad r_{\mu\upsilon}\in\qty[0,r_c]
\end{gather}

For the force of the swap mechanism, we analyze that is computed using a chain rule,
\begin{align*}
    U_\mathrm{swap}(r)
\end{align*}


\subsection{LAMMPS implementation}

We use reduce units, Lennard-Jones units.

To create the patchy particles, the \verb|zero| bond style is used.
The reason to use this, is because bond forces and energies are not computed, but the geometry of bond pairs is accessible to other commands (\href{https://docs.lammps.org/bond_zero.html}{Ref}).

The pair styles used in the simulation are: \verb|hybrid/overlay|, \verb|zero|, \verb|lj/cut|, \verb|table| and \verb|threebody/table|.
The \verb|hybrid/overlay| style is used because superimposed multiple potentials in an additive fashion (\href{https://docs.lammps.org/pair_hybrid.html}{Ref}).
The rest of pair styles are to implement the potentials described in \ref{subsec:Potentials}.

The length of the box is set, such that the desire Monomers and Cross-Linkers can be spawn.
The mass of the patches are set to be the half mass of the CL and MO.

The \verb|pair_coeff| commands where set to accomplish the simulation describe in \ref{sec:descriptionSimulation}.
With respect the \verb|create_atoms| command, the \textit{overlap} keyword was assign to a value of the diameter of CL and MO.

Then, the \verb|rigid/small| fix command is used to create the Monomers and Cross-Linkers particles.
This is because, this command is typucally best for a system with large number of small rigid bodies\href{https://docs.lammps.org/fix_rigid.html}{Ref}.

The \verb|neighbor| command was set of type bin with a value of 1.8 and the \verb|neigh_modify| command with the exclude keyword was added to save needless computation due to the rigid bodies (\href{https://docs.lammps.org/neigh_modify.html}{Ref}).

Then, a Langevin thermostat is used with a velocity-Verlet time integration algorithm to perform Brownian dynamics with the commands \verb|fix lagevin| and \verb|fix nve|.
The Langevin thermostat is implemented to models an interaction with a background implicit solvent, in this case water.
Meanwhile, the \verb|fix nve| help to create a system trajectory consistent with the microcanonical ensemble, in which the number of particles, volume and energy remains constant.

finally, multiple \verb|computes| are used to get the potential, kinetic and total energies, temperature and voronoi analysis.

\subsection{Packing fraction}

To approximate a desire packing fraction in the simulation we consider that the packing fraction represent the ratio between the volume of the particle with respect the total volume of the simulation box,
\begin{gather*}
    \phi = \frac{V_{\mathrm{particles}}}{V_\mathrm{box}}.
\end{gather*}
Since, the packing fraction and the volume of the particles are defined, we compute for the volume of the simulation box, and then assume that the simulation box is a cube.

We use a ``ghost'' particle to compute the approximate volume, due to easier calcalculations.
We assume a sphere of $r_{\mathrm{CP}}+r_{\mathrm{patch}}$ and compute the volume of that ``ghost'' sphere.
\begin{gather*}
    V_{\mathrm{ghost}} = \frac{3}{4}\pi (r_{\mathrm{CP}}+r_{\mathrm{patch}})^{3}
\end{gather*}
considering that $r_{\mathrm{CP}}=0.5, r_{\mathrm{patch}}=0.2$, the volume is,
\begin{align*}
    V_{\mathrm{ghost}} &= \frac{3}{4}\pi (0.7)^{3} \\
                       &= 0.8.
\end{align*}

Now, to compute the dimensions of the simulation box,
\begin{align*}
    V_\mathrm{box} &= \frac{V_{\mathrm{particles}}}{\phi} \\
                   &= \frac{0.8}{\phi} \\
    \frac{V_\mathrm{box}}{3}&= \frac{1}{3}\frac{0.8}{\phi} \\
    L &= \frac{0.8}{3\phi}
\end{align*}

\end{document}
